\documentclass[a7paper,print,10pt,grid=both]{kartei}
\usepackage[utf8]{inputenc}
\usepackage{aurical}
\usepackage[english]{babel}

\renewcommand{\antwort}{Effect}
\renewcommand{\dieantwort}{Effect}

\include{macros}

\begin{document}

% ---------- Additional Cards --------------------
%
\card{NPC}{Norre the Hunter}{
  An old but veteran werewolf hunter. He has a special distaste and hatred
  towards feys and druids.
}{
  \profession{Hunter}
  \bonus{+1 stability, +1 security against fey/druid}
  \malus{-2 WP per week}
}
\card{NPC}{Tormin the Smith}{
  The old dwarf still knows how to swing a hammer. At least, if he is sober
  enough to hit the anvil.
}{
  \profession{Smith}
  \cost{-2 WP per week}
}
% Supersedes the old Hunter's Lodge that didn't require a hunter
\card{Building I}{Hunter's Lodge}{
  A hunter's lodge provides fresh meat for the tavern, as well as
  selling off furs and hide for extra profit. The hunters also aid in
  fending off dangerous animals and beasts.
}{
  \requires{Hunter}
  \cost{30 WP}
  \bonus{5 WP per week, +1 security against beasts}
}
\card{Building I}{Forge and Steel}{
  Simple forge and steel, to smelt and work iron or steel. Allows a dedicated
  smith to create and repair simple items, and take care of horses that might
  need new shoes.
}{
  \requires{Smith}
  \cost{30 WP}
  \bonus{5 WP per week, +1 stability}
}
\card{Building II}{Smithy}{
  A properly stocked smithy capable of produding, repairing and
  maintaining a wide variety of metal goods, including weapons, armour
  and building materials.
}{
  \requires{Smith}
  \cost{70 WP}
  \bonus{10 WP per week, +1 security, +1 stability}
}
\card{Building III}{Arcane Workshop}{
  Enhances the smithy to an arcane workshop, capable of forging arcane creations
  such as golems, arcane arms and armour, as well as advanced Everblack based
  creations.
}{
  \requires{Arcane Black Smith}
  \cost{200 WP}
  \bonus{15 WP per week, +2 security, +2 stability}
}
\card{Problem}{Fey Infestation}{
  A group of fey have made the surrounding woods their home. They are harassing,
  or even openly attacking farmers, workers and traders.
}{
  \dc{Security}{15}
  \ignored{-1 security, -1 stability}
}
\card{Problem}{Trade Feud}{
  Some traders have taken it upon themselves to eliminate competition. This feud
  should be curbed in its infancy before it turns violent.
}{
  \dc{Stability}{15}
  \ignored{-2 stability}
}

\end{document}
