\documentclass[a7paper,print,10pt,grid=both]{kartei}
\usepackage[utf8]{inputenc}
\usepackage{aurical}
\usepackage[english]{babel}
\usepackage{niceframe}
\usepackage{amssymb}

\renewcommand{\antwort}{Effect}
\renewcommand{\dieantwort}{Effect}

\newcommand{\entry}[2]{%
  \vspace{0.1cm}
  \Large{\textbf{#1:} #2} \\
  \vspace{0.1cm}
}

\newcommand{\bonus}[1]{\entry{Bonus}{#1}}
\newcommand{\requires}[1]{\entry{Requirs}{#1}}
\newcommand{\malus}[1]{\entry{Penalty}{#1}}
\newcommand{\dc}[2]{\entry{#1 DC}{#2}}
\newcommand{\success}[1]{\entry{Success}{#1}}
\newcommand{\failure}[1]{\entry{Failure}{#1}}
\newcommand{\ignored}[1]{\entry{Ignored}{#1}}
\newcommand{\cost}[1]{\entry{Cost}{#1}}

\newcommand{\card}[4]{%
  \begin{karte}[\textbf{#1}]{
      \center{
        \vspace*{-1.0cm} \textbf{#2}
        \par
        \vspace*{+1.0cm}
        \small{\emph{#3}}
        \vspace*{\fill}
      }
    }
    \vspace*{\fill}
    \center{#4}
    \vspace*{\fill}
  \end{karte}
}

\begin{document}

% ---------- Initial cards ---------------------------
%
\card{NPC}{Torek the Keghauler}{%
  One hulk of an half-orc as a bartender. Quite capable of carrying
  hefty mugs of ale and rum, and smashing heads. But not quite so
  pleasant on the eyes.
}{
  \bonus{+1 security}
  \malus{-2 WP per week}
}
\card{NPC}{Anarelia the Barmaid}{
  Anarelia was Torek's personal slave and barmaid, but is now free due
  to Arvid's laws regarding slavery. Hard and earnest worker, if a bit
  feisty.
}{
  \bonus{+1 attraction}
  \malus{-1 WP per week}
}
\card{Building I}{Smuggler's Tavern}{%
  ``The landlord's a bastard, the barmaid's a whore \\
  but give them no shit or you're straight out the door'' \\
  -- Alestorm
}{
  \requires{bartender}
  \bonus{2 WP income per week}
  \malus{-2 stability}
}
\card{Building I}{Simple Docks}{%
  Perfect for smaller ships, such as boats and schooners.
}{\bonus{2 WP income per week}}

\card{Building I}{Dilettantish Defences}{%
  Hastily erected fortifications which are barely able to keep wild
  animals from wandering into the camp.
}{\bonus{+1 security}}

\card{Building I}{Small Stables}{
  Perfect for horses and drunk cheapskates that can't afford a room.
}{\bonus{1 WP income per week}}
% -----------------------------------------------------------------------

% ----------------------- BUILDINGS -------------------------------------
%
\card{Buiding II}{Harbour Café}{%
  Upgrade the tavern to a finer establishment, that also serves out luxury
  drink and food such as coffee, tea and fine meals.

  ``Come take a drink and drown your sorrows, \\
  and all our fears will be gone 'til tomorrow \\
  Have no regrets, and live for the day \\
  In Nancy's Harbour Café'' -- Alestorm
}{
  \cost{100 WP}
  \requires{bartender,cook}
  \bonus{10 WP per week}
  \bonus{+4 attraction}
  \bonus{+1 stability}
}
\card{Building II}{Brothel}{%
  Upgrade the tavern to a whorehouse.

  ``It's a den of debauchery, violence and sin.'' -- Alestorm
}{
  \cost{100 WP}
  \requires{5 wenches, dedicated security}
  \bonus{20 WP per week}
  \bonus{+2 attraction}
  \bonus{-4 stability}
}
\card{Building I}{Outlying Farm}{
  You know own one of the outlying farms and thus get a share of the crops,
  meat and other produce from the fertile soil of the land.
}{
  \cost{50 WP}
  \bonus{5 WP per week}
  \bonus{+1 attraction}
}
\card{Building I}{Upper Floor with Rooms}{
  Upgrade the tavern with another floor, adding rooms that can be rented out
  to patrons. Although minimal in luxury, they are more comfortable
  than sleeping in the chairs and on tables.
}{
  \cost{40 WP}
  \bonus{4 WP per week}
}
\card{Building I}{Wine Cellar}{
  A wine cellar. Great for storing wines of all ages and types, as well as
  holding secret meetings and hiding illegal things that no one should see.
}{
  \cost{40 WP}
  \bonus{+2 attraction}
  \bonus{+1 stability}
}
\card{Building II}{Harbour}{
  Upgrade the docks to a proper harbour area, with cranes, loading ports and
  additional jetties for larger ships.
}{
  \cost{50 WP}
  \bonus{10 WP per week}
  \bonus{+2 attraction}
}
\card{Building II}{Wooden Wall}{
  A proper wooden wall to keep all the bastards away.
}{
  \cost{50 WP}
  \bonus{+3 security}
}
\card{Building I}{Harbour Defences}{
  Lookout posts and arrow towers for rudimentary defence of the harbour.
}{
  \cost{30 WP}
  \requires{dedicated security}
  \bonus{+2 security}
}
\card{Building I}{Brig}{
  A small area to hold and lookup ne'er-do-wells and other criminals.
}{
  \cost{40 WP}
  \requires{dedicated security}
  \bonus{+2 security}
  \bonus{+2 stability}
}
% ------------------- CRISIS --------------------------------------------
% Sea incursions from the Savage Lands, and invasions
%
\card{Crisis}{Small Sea Incursion}{
  A small group of orc pirates from \emph{Iâfandir} attempt to raid the
  coast of \emph{Eilean Mor}.
}{
  \dc{Security}{15}
  \cost{40 WP}
  \success{+1 defence, 5 WP}
  \failure{-1 defence, -5 WP}
}
\card{Crisis}{Sea Raid}{
  A small group of bugbear slavers from \emph{Iâfandir} attempt to raid the
  coast of \emph{Eilean Mor} for some new slaves to take back home.
}{
  \dc{Security}{20}
  \cost{80 WP}
  \success{+2 defence, +50 WP}
  \failure{-2 defence, -50 WP}
}
\card{Crisis}{Savage Invasion}{
  A large fleet of bugbear warriors from \emph{Iâfandir} are invading
  and pillaging the coastal area.
}{
  \dc{Security}{25}
  \cost{200 WP}
  \success{+5 defence, +100 WP}
  \failure{-5 defence, -100 WP}
}
\card{Crisis}{Lord Norello Invades}{
  An army of Lord Norello's finest are invading the land trying to reclaim the
  vital sea port, and the strategic location of the tavern.
}{
  \dc{Security}{25}
  \cost{WP}{400}
  \failure{Subjugation beneath Norello's rule}
}
\card{Crisis}{Norbury Invades}{
  You did it! You drew the ire of a city kingdom and now they want what you
  have. The well trained navy and army of Norbury is at your doorsteps.
}{
  \dc{Security}{35}
  \cost{WP}{1000}
  \failure{Subjugation beneath Norbury's rule}
}
% ----------------------------------------------------------------------------

% ---------------------- PROBLEMS --------------------------------------------
%
\card{Problem}{Nasty Rumour}{
  A nasty rumour has spread about the tavern or its owners. Unless counter
  acted it will surely keep patrons away
}{
  \dc{Attraction}{10}
  \ignored{-1 attraction}
}
\card{Problem}{Repeated Fights}{
  Bar fights are a common occurrence in the tavern, causing the more
  tender patrons to stay away.
}{
  \dc{Stability}{10}
  \ignored{-1 stability}
}
\card{Problem}{Drug Den}{
  Drug trade and drug use has become an open secret within the tavern, giving
  it a foul reputation.
}{
  \dc{Attraction}{15}
  \ignored{-2 stability, -2 attraction}
  \failure{-2 attraction}
}
\card{Problem}{Roaming Bandits}{
  Bandits threaten the security of the land trade routes and routinely attack
  and rob merchants.
}{
  \dc{Security}{15}
  \ignored{-2 security}
  \failure{-2 security}
}
\card{Problem}{Wild Beasts}{
  Wild beasts roam the land outside the tavern, slaughtering life
  stock and threatening both merchants and farmers.
}{
  \dc{Security}{13}
  \ignored{-1 security}
  \failure{-1 security}
}
\card{Problem}{Shapers of the Three Kings}{
  Shaper creatures (were- warriors) of the Three Kings roam the
  lands in search for blood and glory. They openly attack everyone,
  threatening both traders and civilians.
}{
  \dc{Security}{22}
  \ignored{-5 security}
  \failure{-5 security}
}
\card{Problem}{Preacher of the Seas}{
  A priest of Isamir, the beast of the seas, protests the vile defilement the
  harbour and its ships represents towards the sea.
}{
  \dc{Stability}{15}
  \ignored{-2 stability}
}
\card{Problem}{Pleb Unrest}{
  The farmers, workers and inhabitants of the surrounding sea are protesting
  their treatment beneath Lord Norello's rule, and demand security, stability
  and lower taxes.
}{
  \dc{Stability}{20}
  \ignored{All external buildings stop producing WP}
  \ignored{-2 stability}
  \failure{-5 stability}
}
\card{Problem}{Scraping the Barrel}{
  The ``good stuff'' has run out, and there is no longer any hard liquor
  available to the patrons.
}{
  \dc{Stability}{13}
  \ignored{-5 WP per week, -2 attraction}
  \failure{-10 WP}
}

% ----------------------------------------- NPCS --------------------------
\card{NPC}{Lanis the Honourable Captain}{
  Lanis, a truly honourable captain, has sailed the seas both north
  and east of \emph{Eilean Mor}. He has been known to undertake shadier
  dealings, but is a good earner.
}{
  \bonus{+5 WP per week}
  \malus{-1 stability}
}
\card{NPC}{Talia of Norbury}{
  The Norbury envoy responsible for all lands bordering the city kingdom.
  The snow elven lady is highly charismatic, and is your diplomatic
  link to your eastern neighbours.
}{
  \provides{dedicated diplomacy}
  \bonus{+4 attraction (Norbury)}
  \bonus{-4 attraction (Arvid)}
}
\card{NPC}{Corporal Bertram Carpel}{
  A human corporal from Arvid called Betram Carpel has been assigned to you
  as an envoy to represent the security interests of Arvid.
}{
  \provides{dedicated security}
  \bonus{+2 stability}
  \bonus{+2 attraction (Arvid)}
}

% ----------------------------------------- Opportunities ----------------
\card{Opportunity}{Three Holy Sisters}{
  Three priestess of \emph{Nyddwr} make a stop at your tavern, requesting
  food, lodging and a place to give out readings of the past, present and
  future. They are only staying for a few days before moving.
}{
  \bonus{+5 attraction}
  \bonus{+3 stability}
  \malus{-3 WP for their lodging}
}
\card{Opportunity}{Washed Ashore}{
  Another sea raid from \emph{Iâfandir} has been crushed and sunk off the cost
  by the \emph{Norbury} navy. Now floatsam, and perhaps a surprise, are being
  washed ashore at the harbour.
}{
  \bonus{5 WP}
  \bonus{12\% chance on finding a survivor}
}
\card{Opportunity}{Festival}{
  Wandering musicians and performers have entered your tavern, and are
  performing for your customers. They are staying for a few days before moving
  on.
}{
  \bonus{+2 attraction}
  \bonus{+2 WP}
}
\card{Opportunity}{Coastal Gold}{
  Some fishermen have claimed that a particularly valuable floatsam has washed
  ashore somewhere along the coast. Claiming it could be beneficial.
}{
  \dc{Security}{10}
  \success{10 WP}
  \failure{-1 security}
}
\card{Opportunity}{Coastal Treasure}{
  Some fishermen have claimed that a particularly valuable floatsam has washed
  ashore somewhere along the coast. Claiming it could be beneficial.
}{
  \dc{Security}{15}
  \success{30 WP}
  \failure{-2 security}
}
\card{Opportunity}{Costal Wealth}{
  Some fishermen have claimed that a particularly valuable floatsam has washed
  ashore somewhere along the coast. Claiming it could be beneficial.
}{
  \dc{Security}{18}
  \success{50 WP}
  \failure{-3 security}
}

\end{document}
